Make any stupid plot you want

### 2021-01-20 draft/sections/math.tex
transitions

\begin{figure}
    %%include transition function sketch
\end{figure}

We can represent more complex spaces with transition functions that are maps from the fiber to the fiber along the edges. can also fold in if monoid is commutative on transition function:

>>>>

\begin{figure}
    \label{fig:data_base_transition}
    \includegraphics[width=\textwidth]{figures/math/transition_functions.png}
    \caption{Many non-trivial spaces can be made locally trivial by dividing $E$ into subspaces and defining transition functions between the edges on K for how to glue the two subspaces such that the sigmas are continuous.}
\end{figure}

We can represent some spaces that are not trivial as

with transition functions that are maps from the fiber to the fiber along the edges. can also fold in if monoid is commutative on transition function:
